Segmentation of Electron Microscopy Images for Connectomics

### 2018-05-02 papers/quals2018/0_introduction.tex
updates to qualifying exam

One of the critical components of connectomics---the field concerned with reconstructing the wiring diagram of the brain at nanometer resolution---is automatic segmentation of electron microscopy (EM) images of the brain.
With recent advances in EM acquisition techniques, neuroscientists can now generate a terabyte of image data every hour~\cite{richard2016imaging}.
These images are typically anisotropic with $4$nm resolution in the $xy$ plane and \numrange{30}{40}nm between slices. 
At this resolution, we can see the axon terminals and dendritic spines, and the synaptic connections between them.
Accurate reconstruction of every neuron paired with synapse detection will allow us to create a true graphical representation of the brain and further our understanding of the underlying circuitry.
These segmentation, or label, volumes assign a 32- or 64-bit integer label to every voxel where voxels have the same label only if they belong to the same neuron.

An ambitious manual reconstruction effort in the 1980s resulted in the first complete connectome of any animal, the \textit{Caenorhabditis elegans} worm~\cite{white1986structure}. 
This species has 302 neurons and manual labeling required several years.
More recent studies focus on \textit{Drosophila} flies~\cite{jovanic2016competitive,takemura2015synaptic},  rodents~\cite{richard2016imaging}, and even humans~\cite{sporns2005human}. 
With an EM throughput of one terabyte per hour, neuroscientists can image a cubic millimeter of data (two petabytes) in six months~\cite{suissa2016automatic}. 
At this scale, the manual reconstruction techniques of the 80s are simply infeasible.
Thus, researchers rely on deep learning methods to segment these massive datasets.

Automatic reconstruction produces label volumes that, uncompressed, are much larger in size than the already massive image datasets.
In our paper published in \textit{MICCAI 2017}, we explore the effectiveness of existing general-purpose, image, and video compression techniques on the segmentation datasets.
We find that these existing techniques fail to adequately exploit the typical properties of our label volumes.
Thus, we propose \textit{Compresso}, a new compression algorithm specifically tailored for large label volumes that far exceeds existing strategies.

Automatic reconstruction techniques need to be fast, scalable, and accurate.
Ideally, image acquisition is the bottleneck of the connectomics pipeline so reconstruction occurs at a rate of one terabyte per hour~\cite{haehn2017scalable}.
We can achieve this throughput with parallelization among several GPUs with existing techniques~\cite{funke2017deep,parag2017anisotropic}.
However, these automatic methods typically only rely on local context for decision making and are agnostic about the underlying biological systems.
Thus, they often make errors at scale and currently require human proofreading or other error correction techniques~\cite{haehn2017guided,error_correction_using_CNN}.

>>>>

One of the critical components of connectomics---the field concerned with reconstructing the wiring diagram of the brain at nanometer resolution---is automatic segmentation of electron microscopy (EM) images.
With recent advancements in EM acquisition techniques, neuroscientists can now generate a terabyte of image data every hour~\cite{richard2016imaging}.
These images are typically anisotropic with $4$nm resolution in the $xy$ plane and \numrange{30}{40}nm between slices. 
At this resolution, we can see the axon terminals and dendritic spines, and the synaptic connections between them.
Neuroscientists hope to further their understanding of the brain's underlying circuitry with accurate reconstructions of every neuron in these volumes and classification of the synaptic connections.

An ambitious manual reconstruction effort in the 1980s resulted in the first complete connectome of any animal, the \textit{Caenorhabditis elegans} worm~\cite{white1986structure}. 
This species has 302 neurons and manual labeling required several years.
More recent studies focus on \textit{Drosophila} flies~\cite{jovanic2016competitive,takemura2015synaptic},  rodents~\cite{richard2016imaging}, and even humans~\cite{sporns2005human}. 
With an EM throughput of one terabyte per hour, neuroscientists can image a cubic millimeter of data (two petabytes) in six months~\cite{suissa2016automatic}. 
At this scale, the manual reconstruction techniques of the 80s are simply infeasible.
Thus, researchers rely on machine learning methods to segment these massive datasets.

Automatic reconstruction produces label volumes that, uncompressed, are much larger in size than the already massive image datasets.
These label volumes assign a 32- or 64-bit integer to every voxel where voxels have the same label only if they belong to the same neuron.
In our paper published in \textit{MICCAI 2017}, we explore the effectiveness of existing general-purpose, image, and video compression techniques on the segmentation datasets.
We find that these existing techniques fail to adequately exploit the typical properties of our label volumes.
Thus, we propose \textit{Compresso}, a new compression algorithm specifically tailored for large label volumes that far exceeds existing strategies.

\begin{figure}
	\includegraphics[width=\linewidth]{./figures/proposal-header.png}
	\caption{From an EM image stack, 3D CNNs generate affinities between voxels (left). These affinities are agglomerated into superpixels which in turn are merged to form a complete segmentation (center). Oftentimes these methods produce errors and thus require error correction to improve the accuracy (right).}
	\label{fig:overview}
\end{figure}

Automatic reconstruction techniques need to be fast, scalable, and accurate.
Ideally, image acquisition is the bottleneck of the connectomics pipeline so reconstruction occurs at a rate of one terabyte per hour~\cite{haehn2017scalable}.
We can achieve this throughput with parallelization among several GPUs with existing techniques~\cite{funke2017deep,parag2017anisotropic}.
However, these automatic methods typically rely on local context for decision making and are agnostic about the underlying biological systems.
Thus, they often make errors at scale and currently require human proofreading or other error correction techniques~\cite{haehn2017guided,error_correction_using_CNN}.

### 2018-05-02 papers/quals2018/1_related_work.tex
updates to qualifying exam

\begin{figure*}[t]
	\begin{center}
		\includegraphics[width=0.45\linewidth]{./figures/encoding_diagram_opt.pdf}
		\hspace{0.08\linewidth}
		\includegraphics[width=0.45\linewidth]{./figures/window_values.pdf}
	\end{center}	
	\caption{Compresso works by dividing up the segmentation data into small blocks. On the left we show the intersection of three segments in a $4\times4\times1$ window. We extract a boundary map from this segmentation to transform the window into an integral value between $0$ and $2^{16} - 1$. The location $i$ requires some additional bookkeeping. On the right are the $100$ most common $8 \times 8 \times 1$ windows accounting for $\sim82\%$ of the volume on a representative dataset.}
	\label{fig:compression}
\end{figure*}

@@

Additional research builds on top of these region-based methods to correct errors in the segmentation. This can be done either using human proofreading~\cite{haehn2017guided,haehn2014design,mojo2} or automatically~\cite{rolnick2017morphological,error_correction_using_CNN}. 
In both cases, available methods are pixel-based and do not include global biological constraints into the decision making process. 
Our method can take as input any existing segmentation pipeline.

>>>>

Large scale image datasets requires fast automatic segmentation methods to match the throughput of the microscope.
Thus, compressing the data in an efficient manner and accurately constructing the volumes at reasonable speeds become important problems.
Here we provide a brief overview of existing compression methods and reconstruction techniques for these label volumes.

@@

Additional research builds on top of these region-based methods to correct errors in the segmentation. 
These input segmentations can contain two types of errors.
In a \textit{split error}, one neurons contains multiple labels.
In a \textit{merge error}, two or more neurons receive the same label.
This can be done either using human proofreading~\cite{haehn2017guided,haehn2014design,mojo2} or automatically~\cite{rolnick2017morphological,error_correction_using_CNN}. 
In both cases, available methods are pixel-based and do not include global biological constraints into the decision making process. 
Our method can take as input any existing segmentation pipeline.

### 2018-05-02 papers/quals2018/2_method.tex
updates to qualifying exam

% !TEX root =  paper.tex
\section{Biologically-Constrained Error Correction}

\begin{figure*}[t!]
	\centering
	\includegraphics[width=0.75\linewidth]{./figures/teaser_v4.png}
	\caption{Our framework uses both geometric and topological biological constraints for region merging. We (a) generate a simplified graph from the skeleton representation of the input segmentation, (b) train a classifier to learn the edge weight based on the shape of the segment connection, and (c) perform graph partitioning with acyclic constraints.}
	\label{fig:teaser_pipeline}
\end{figure*}

Our method is illustrated in Fig.~\ref{fig:teaser_pipeline}.
From the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with weights $w_e$. 
The nodes correspond to labeled segments from the input data with edges between merge candidates.
We propose the following three steps to formulate and then partition the graph while obeying constraints from the underlying biology.
First, we only consider merging segments based on a skeletonized representation of the input segmentation (Fig.~\ref{fig:teaser_pipeline}a).
This enables us to reduce the number of edges in the graph based on prior knowledge on the shape of neuronal processes.
Second, we train a convolutional neural network that learns biological constraints based on the shapes of the input segmentation (Fig.~\ref{fig:teaser_pipeline}b).
This network generates probabilities that segments belong to the same neuron based only on the segmentations. 
An example of one such learned constraint is that neurons have small turning radii (Fig.~\ref{fig:turn-radii}).
Third, we partition the graph using a lifted multicut formulation with additional acyclic constraints to enforce global biological constraints (Fig.~\ref{fig:teaser_pipeline}c).
The lifted multicut solution is globally consistent which we then augment to produce a tree-structured graph.

@@

To predict the probabilities that two segments belong to the same neuron, we train a feed-forward convolutional network with three \textit{VGG-style} convolution blocks~\cite{chatfield2014return} and two fully connected layers before the final sigmoid activation. 
For the input of the network, we extract a cubic region of interest (ROI) around each endpoint $e$ in $\mathbb{S}_c$ as input to the CNN. 
There are three channels corresponding to voxels belonging to label one, label two, or either label.
We do not use the raw EM image information to avoid the need to retrain the network on datasets that have been stained differently or imaged at different resolution. 
This reduces the need for generating costly manually-labeled ground truth.

\subsection{Optimization-Based Graph Partition}

@@

We need to convert the probabilities into the following weighting scheme to solve the multicut problem with this heuristic~\cite{andres2011probabilistic,keuper2015efficient}.
Given the probability that the nodes belong to the same neuron is $p_e$, the edge weight $w_e$ is defined as
%p_e &=\mbox{CNN}(x_1, x_2) \\
\begin{align}
w_e = \log{\frac{p_e}{1 - p_e}} + \log{\frac{1 - \beta}{\beta}},
\end{align}
where $\beta$ is a tunable parameter that encourages over- or under-segmentation. 
Since, there are many more lifted edges than adjacent edges, we scale down the lifted weights proportionally to their total number  
~\cite{beier2017multicut}.

@@

>>>>

% !TEX root =  paper.tex
\section{Biologically-Constrained Region Merging}

\begin{figure*}[t!]
	\centering
	\includegraphics[width=0.65\linewidth]{./figures/teaser_v4.png}
	\caption{Our framework uses both geometric and topological biological constraints for region merging. We (a) generate a simplified graph from the skeleton representation of the input segmentation, (b) train a classifier to learn the edge weight based on the shape of the segment connection, and (c) perform graph partitioning with acyclic constraints.}
	\label{fig:teaser_pipeline}
\end{figure*}

\begin{figure}[t]
	\centering
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/skeleton1.png}		
	\end{minipage}
	\hfill
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/skeleton2.png}		
	\end{minipage}
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/skeleton3.png}		
	\end{minipage}
	\hfill
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/skeleton4.png}		
	\end{minipage}
	\caption{Example skeletons (in black) extracted from segments using a variant of the TEASER algorithm~\cite{sato2000teasar}. These skeletons not only capture the shape of the segmentation, but also provide endpoints useful for region merging proposals.}
	\label{fig:skeletonization}
\end{figure}

Automatic reconstruction methods need to be fast enough to scale to petabyte datasets while still maintaining a high-level of accuracy.
The most accurate methods, like flood-filling networks~\cite{januszewski2016flood}, are too slow to scale. 
Unfortunately, methods that can scale to petabyte datasets typically rely on only local context and can produce errors at scale~\cite{haehn2017scalable}. 
Therefore, it is necessary to employ error correction strategies on the segmentations from current reconstruction pipelines.
We propose a biologically-constrained region merging algorithm to correct \textit{split errors} in the initial segmentation.

For our proposed method (Fig.~\ref{fig:teaser_pipeline}), from the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with weights $w_e$. 
The nodes correspond to labeled segments from the input data with edges between merge candidates.
We propose the following three steps to formulate and then partition the graph while obeying constraints from the underlying biology.
First, we only consider merging segments based on a skeletonized representation of the input segmentation (Fig.~\ref{fig:teaser_pipeline}a).
This enables us to reduce the number of edges in the graph based on prior knowledge on the shape of neuronal processes.
Second, we train a convolutional neural network that learns biological constraints based on the shapes of the input segmentation (Fig.~\ref{fig:teaser_pipeline}b).
This network generates probabilities that segments belong to the same neuron based only on the segmentations. 
An example of one such learned constraint is that neurons have small turning radii (Fig.~\ref{fig:turn-radii}).
Third, we partition the graph using a lifted multicut formulation with additional acyclic constraints to enforce global biological constraints (Fig.~\ref{fig:teaser_pipeline}c).
The lifted multicut solution is globally consistent which we then augment to produce a tree-structured graph.

@@

To predict the probabilities that two segments belong to the same neuron, we train a feed-forward convolutional network with three \textit{VGG-style} convolution blocks~\cite{chatfield2014return} and two fully connected layers before the final sigmoid activation. 
For the input of the network, we extract a cubic region of interest (ROI) around each midpoint in $\mathbb{S}_c$ as input to the CNN. 
There are three channels corresponding to voxels belonging to label one, label two, or either label.
We do not use the raw EM image information to avoid the need to retrain the network on datasets that have been stained differently or imaged at different resolution. 
This reduces the need for generating costly manually-labeled ground truth. 
\begin{figure}[t]
	\begin{minipage}{0.4\linewidth}
		\includegraphics[width=\linewidth]{./figures/constraint_error.png}
	\end{minipage}
	\hfill
	\begin{minipage}{0.55\linewidth}
		\includegraphics[width=\linewidth]{./figures/constraint_success.png}
	\end{minipage}
	\caption{Geometric constraints for region merging. We show two region merging proposals. On the left, the segments do not belong to the same neuron, as evidenced by the sharp turning radius indicated by the arrow; while on the right, the segments should be merged due to the continuity of the 3D shape. Instead of using handcrafted geometric features, we train a convolutional neural networks to automatically learn them from the ground truth labels.}
	\label{fig:turn-radii}
\end{figure}

\begin{figure}[t]
	\centering
	\begin{minipage}{0.32\linewidth}
		\includegraphics[width=\linewidth]{./figures/split_error1.png}		
	\end{minipage}
	\hfill
	\begin{minipage}{0.32\linewidth}
		\includegraphics[width=\linewidth]{./figures/split_error2.png}				
	\end{minipage}
	\hfill
	\begin{minipage}{0.32\linewidth}
		\includegraphics[width=\linewidth]{./figures/split_error3.png}
	\end{minipage}
	\caption{Three erroneously split segments.}
	\label{fig:merge_candidates}
\end{figure}
\subsection{Optimization-Based Graph Partition}

@@

We need to convert the probabilities into the following weighting scheme to solve the multicut problem with the greedy-edge heuristic~\cite{andres2011probabilistic,keuper2015efficient}.
Given the probability that the nodes belong to the same neuron is $p_e$, the edge weight $w_e$ is defined as
%p_e &=\mbox{CNN}(x_1, x_2) \\
\begin{align}
w_e = \log{\frac{p_e}{1 - p_e}} + \log{\frac{1 - \beta}{\beta}},
\end{align}
where $\beta$ is a tunable parameter that encourages over- or under-segmentation. 
Since, there are many more lifted edges than adjacent edges, we scale down the lifted weights proportionally to their total number  
~\cite{beier2017multicut}.

@@

\begin{figure*}[t!]
	\centering
	\includegraphics[width=0.32\linewidth]{./figures/benchmark/voi-Kasthuri-Luigi-Test.pdf}
	\includegraphics[width=0.32\linewidth]{./figures/benchmark/voi-FlyEM-Vol--1.pdf}
	\includegraphics[width=0.32\linewidth]{./figures/benchmark/voi-FlyEM-Vol--2.pdf}
	\caption{Segmentation benchmark results on three volumes. We compare our method (red) to the baseline segmentation (green) and an oracle (blue) that optimally partitions our constructed graph from our method. Lower VI scores are better. Our method improves the segmentation accuracy over the baseline in all cases.
		Note that our model is only trained on the Kasthuri training volume and it generalizes well to the FlyEM dataset.}
	\label{fig:variation-of-information}
\end{figure*}

### 2018-05-02 papers/quals2018/3_evaluation.tex
updates to qualifying exam

\begin{figure}[t]
	\centering
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/skeleton1.png}		
	\end{minipage}
	\hfill
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/skeleton2.png}		
	\end{minipage}
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/skeleton3.png}		
	\end{minipage}
	\hfill
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/skeleton4.png}		
	\end{minipage}
	\caption{Example skeletons (in black) extracted from segments using a variant of the TEASER algorithm~\cite{sato2000teasar}. These skeletons not only capture the shape of the segmentation, but also provide endpoints useful for region merging proposals.}
	\label{fig:skeletonization}
\end{figure}

\begin{figure}[t]
	\begin{minipage}{0.4\linewidth}
		\includegraphics[width=\linewidth]{./figures/constraint_error.png}
	\end{minipage}
	\hfill
	\begin{minipage}{0.55\linewidth}
		\includegraphics[width=\linewidth]{./figures/constraint_success.png}
	\end{minipage}
	\caption{Geometric constraints for region merging. We show two region merging proposals. On the left, the segments do not belong to the same neuron, as evidenced by the sharp turning radius indicated by the arrow; while on the right, the segments should be merged due to the continuity of the 3D shape. Instead of using handcrafted geometric features, we train a convolutional neural networks to automatically learn them from the ground truth labels.}
	\label{fig:turn-radii}
\end{figure}

\begin{figure}[t]
	\centering
	\begin{minipage}{0.32\linewidth}
		\includegraphics[width=\linewidth]{./figures/split_error1.png}		
	\end{minipage}
	\hfill
	\begin{minipage}{0.32\linewidth}
		\includegraphics[width=\linewidth]{./figures/split_error2.png}				
	\end{minipage}
	\hfill
	\begin{minipage}{0.32\linewidth}
		\includegraphics[width=\linewidth]{./figures/split_error3.png}
	\end{minipage}
	\caption{Three erroneously split segments.}
	\label{fig:merge_candidates}
\end{figure}

@@

Our proposed method is designed for very large connectomics datasets. 
Popular challenge datasets such as CREMI and SNEMI3D are simply too small for any noticeable change. 
The following datasets contain 4 times more volume than the CREMI datasets. 
The first, which we call the Kasthuri dataset, consists of scanning electron microscope images of the neocortex of a mouse brain~\cite{kasthuri2015saturated}. 
This dataset is $5342 \times 3618 \times 338$ voxels in size. 
The resolution of the dataset is $\SI[product-units=single]{3 x 3 x 30}{\nano\meter}^3$ per voxel. 
We divide the dataset into two volumes (Vol. 1 and Vol. 2) along the $x$ dimension, where each volume is $\SI[product-units=single]{8.0 x 10.9 x 10.1}{\micro\meter}^3$.
We train one of these halves and test on the other.
Our second dataset, called FlyEM, comes from the mushroom body of a 5-day old adult male \textit{Drosophila} fly imaged by a focused ion-beam milling scanning electron microscopy~\cite{takemura2017connectome}.
The original dataset contains a $\SI[product-units=single]{40 x 50 x 120}{\micro\meter}^3$ volume with a resolution of $\SI[product-units=single]{10 x 10 x 10}{\nano\meter}^3$ per voxel. 
We use two cubes (Vol. 1 and Vol. 2) of size $\SI[product-units=single]{10 x 10 x 10}{\micro\meter}^3$.

\subsection{Method Configuration}
\noindent\textbf{Initial Segmentation}
The segmentation of the Kasthuri dataset is computed by agglomerating 3D supervoxels produced by the z-watershed algorithm from 3D affinity predictions~\cite{zlateski2015image}. 
A recent study by Funke et al.~\cite{funke2017deep} demonstrates superior performance of such methods over existing ones on anisotropic data. 
We learn 3D affinities using MALIS loss with a U-Net~\cite{ronneberger2015u,Turaga:2009}. 
We apply the z-watershed algorithm with suitable parameters to compute a 3D over-segmentation of the volume. 
The resulting 3D over-segmentation is then agglomerated using the technique of context-aware delayed agglomeration to generate the final segmentation~\cite{10.1371/journal.pone.0125825}.
For the FlyEM data, based on the authors' suggestion~\cite{takemura2017connectome}, we apply a context-aware delayed agglomeration algorithm~\cite{10.1371/journal.pone.0125825} that shows improved performance on this dataset over the pipeline used in the original publication. 
This segmentation framework learns voxel and supervoxel classifiers with an emphasis to minimize under-segmentation error. 
The algorithm first computes multi-channel 3-D predictions for membranes, cell interiors, and mitochondria, among other cell features. 
The membrane prediction channel is used to produce an over-segmented volume using 3D watershed, which is then agglomerated hierarchically up to a certain confidence threshold. 
We used exactly the same parameters as the publicly available code for this algorithm.
%For the Fib-25 challenge dataset, we use the segmentation from Funke et al. as our input~\cite{funke2017deep}.
\\~\\
\noindent\textbf{Graph Generation}
The two parameters for the graph pruning algorithm (Sec.~\ref{sec:skeletonization}) are $t_{low}$ and $t_{high}$. 
Ideally, our graph will have an edge for every over-segmented pair of labels with few edges between correctly segmented pairs. 
After considering various thresholds, we find that $t_{low} = \SI{210}{\nano\meter}$ and $t_{high} = \SI{300}{\nano\meter}$ produce expressive graphs with a scalable number of nodes and edges.
We explore these thresholds in greater detail in the supplemental material.
During implementation, we use nanometers instead of voxels for these thresholds to have uniform units across all datasets.
% Connectomics datasets often have lower sample resolutions in $z$ because of limitations during sample preparation. 
% Using nanometers allows us to have uniform units across all of these datasets and calculate the thresholds in voxels at runtime.
% Although the voxels vary between different datasets, the physical space remains constant. 
\\~\\
\noindent\textbf{Edge Weight Learning}
\label{sec:network-parameters}
We use half of the Kasthuri dataset for training and validation. 
We train on 80\% of the potential merge candidates for this volume.
We validate the CNN classifier on the remaining 20\% of the candidates. 
Since our input does not require the image data, we can train on the anisotropic Kasthuri data and test on the isotropic FlyEM data.

Since our input is an existing segmentation of the EM images, there are very few training examples compared to per-pixel classifiers that train on a unique window for each voxel. 
The Kasthuri dataset represents a region of brain over $\SI[product-units=single]{800}{\micro\meter}^3$ in volume and only yields 640 positive merge examples and 4821 negative ones.
To avoid overfitting our deep networks, we apply the following augmentations on the training examples.
During a single batch, we randomly select ten positive and ten negative examples. 
With probability 0.5, an example is reflected across the $xy$-plane. 
We then rotate each example by a random angle between $0$ and $360$ degrees using nearest neighbor interpolation. 
The supplemental material contains experiments demonstrating the benefits of this augmentation strategy.
We have 20,000 such examples per epoch.

>>>>

@@

Our first dataset, which we call the Kasthuri dataset, consists of scanning electron microscope images of the neocortex of a mouse brain~\cite{kasthuri2015saturated}. 
This dataset is $5342 \times 3618 \times 338$ voxels in size. 
The resolution of the dataset is $\SI[product-units=single]{3 x 3 x 30}{\nano\meter}^3$ per voxel. 
We divide the dataset into two volumes (Vol. 1 and Vol. 2) along the $x$ dimension, where each volume is $\SI[product-units=single]{8.0 x 10.9 x 10.1}{\micro\meter}^3$.
We train and validate our methods on Vol. 1 and test on Vol. 2.
Our second dataset, called FlyEM, comes from the mushroom body of a 5-day old adult male \textit{Drosophila} fly imaged by a focused ion-beam milling scanning electron microscopy~\cite{takemura2017connectome}.
The original dataset contains a $\SI[product-units=single]{40 x 50 x 120}{\micro\meter}^3$ volume with a resolution of $\SI[product-units=single]{10 x 10 x 10}{\nano\meter}^3$ per voxel. 
We use two cubes (Vol. 1 and Vol. 2) of size $\SI[product-units=single]{10 x 10 x 10}{\micro\meter}^3$.

\subsection{Method Configuration}

\noindent\textbf{Input Segmentation.}
The segmentation of the Kasthuri dataset is computed by agglomerating 3D supervoxels produced by the z-watershed algorithm from 3D affinity predictions~\cite{zlateski2015image}. 
We learn 3D affinities using MALIS loss with a U-Net~\cite{ronneberger2015u,Turaga:2009}. 
We apply the z-watershed algorithm with suitable parameters to compute a 3D over-segmentation of the volume. 
The resulting 3D oversegmentation is then agglomerated using the technique of context-aware delayed agglomeration to generate the final segmentation~\cite{10.1371/journal.pone.0125825}.

For the FlyEM data, based on the authors' suggestion~\cite{takemura2017connectome}, we apply a context-aware delayed agglomeration algorithm~\cite{10.1371/journal.pone.0125825} that shows improved performance on this dataset over the pipeline used in the original publication. 
This segmentation framework learns voxel and supervoxel classifiers with an emphasis to minimize under-segmentation error. 
The algorithm first computes multi-channel 3D predictions for membranes, cell interiors, and mitochondria, among other cell features. 
The membrane prediction channel is used to produce an oversegmented volume using 3D watershed, which is then agglomerated hierarchically up to a certain confidence threshold. 
We used exactly the same parameters as the publicly available code for this algorithm.
\\~\\
\noindent\textbf{Graph Generation.}
The two parameters for the graph pruning algorithm (Sec.~\ref{sec:skeletonization}) are $t_{low}$ and $t_{high}$. 
Ideally, our graph will have an edge for every over-segmented pair of labels with few edges between correctly segmented pairs. 
After considering various thresholds, we find that $t_{low} = \SI{210}{\nano\meter}$ and $t_{high} = \SI{300}{\nano\meter}$ produce expressive graphs with a scalable number of nodes and edges.
During implementation, we use nanometers instead of voxels for these thresholds to have uniform units across all datasets.
\\~\\
\noindent\textbf{Edge Weight Learning.}
\label{sec:network-parameters}
We use half of the Kasthuri dataset for training and validation. 
We train on 80\% of the potential merge candidates for this volume.
We validate the CNN classifier on the remaining 20\% of the candidates. 
Since our input does not require the image data, we can train on the anisotropic Kasthuri data and test on the isotropic FlyEM data.
\\~\\
\noindent\textbf{Training Augmentation.}
Since our input is an existing segmentation of the EM images, there are very few training examples compared to per-pixel classifiers that train on a unique window for each voxel. 
The Kasthuri dataset represents a region of brain over $\SI[product-units=single]{800}{\micro\meter}^3$ in volume and only yields 640 positive merge examples and 4821 negative ones.
To avoid overfitting our deep networks, we apply the following augmentations on the training examples.
During a single batch, we randomly select ten positive and ten negative examples. 
With probability 0.5, an example is reflected across the $xy$-plane. 
We then rotate each example by a random angle between $0$ and $360$ degrees using nearest neighbor interpolation. 
The supplemental material contains experiments demonstrating the benefits of this augmentation strategy.
We have 20,000 such examples per epoch.

### 2018-05-02 papers/quals2018/4_results.tex
updates to qualifying exam

\begin{figure*}[t!]
	\centering
	\includegraphics[width=0.32\linewidth]{./figures/benchmark/voi-Kasthuri-Luigi-Test.pdf}
	\includegraphics[width=0.32\linewidth]{./figures/benchmark/voi-FlyEM-Vol--1.pdf}
	\includegraphics[width=0.32\linewidth]{./figures/benchmark/voi-FlyEM-Vol--2.pdf}
	\caption{Segmentation benchmark results on three volumes. We compare our method (red) to the baseline segmentation (green) and an oracle (blue) that optimally partitions our constructed graph from our method. Lower VI scores are better. Our method improves the segmentation accuracy over the baseline in all cases.
	Note that our model is only trained on the Kasthuri training volume and it generalizes well to the FlyEM dataset.}
	\label{fig:variation-of-information}
\end{figure*}

In Fig.~\ref{fig:variation-of-information}, we show the VI results of the pixel-based reconstructions of the Kasthuri and FlyEM data (Sec.~\ref{sec:dataset}) for varying thresholds of agglomeration (green). 
We use one of these segmentations (green circle) as our input dataset with an agglomeration threshold of 0.3 for all datasets. 
We show comparisons to an oracle (blue) that correctly partitions the graph from our method based on ground truth.

Scores closer to the origin are better for this metric, and in every instance our results are below the green curve.
We see improvements on each data with a reduction in total VI score of $10.4\%$ on the Kasthuri data and $8.9\%$ and $5.4\%$ on the FlyEM datasets.

>>>>

In Fig.~\ref{fig:variation-of-information}, we show the VI results of the pixel-based reconstructions of the Kasthuri and FlyEM data (Sec.~\ref{sec:dataset}) for varying thresholds of agglomeration (green). 
We show comparisons to an oracle (blue) that correctly partitions the graph from our method based on ground truth.
Scores closer to the origin are better for this metric, and in every instance our results (red) are below the green curve.
We see improvements on each data with a reduction in total VI score of $10.4\%$ on the Kasthuri data and $8.9\%$ and $5.4\%$ on the FlyEM datasets.

### 2018-05-02 papers/quals2018/5_proposed.tex
quals: major updates to structure
updates to qualifying exam

\section{Proposed Work}

There are significantly more biological constraints that we plan to use in the future.
Once we improve our synaptic classifiers, we can ensure that we do not merge dendritic spines with axons. 
By stipulating that a segment on one side of the cell body can only have either pre- or post-synaptic connections, we will prevent undersegmentation that merges multiple neurons together.
Additionally, once we have a classifier to label each neuron as inhibitory or excitatory, we can prevent the merging of two different types of neurons.
Both of these additional constraints will help with the current problem associated with large-scale reconstruction.
Namely, that a small percentage of merge errors results in a tangled mess of multiple neurons per segment.

To further prevent this problem, we will augment our work to correct split errors as well.
We will generate locations from splits with the following algorithm.
First, we will locate places where a single skeleton joint has three immediate neighbors (Fig~\ref{fig:split_errors}).
We will choose two of the neighbors as seed locations for a watershed algorithm that will run on the affinities constrained to the segment.
This will generate a potential split location between the two seeds.
We will then extract a region of interest around this split and use that cube as input into our previously trained merge classifier.
If the classifier says that the two segments should not merge, we will accept the split as is and divide the segment.
Otherwise we will ignore this split candidate and keep the segment intact.

A benefit of this approach is that we will have one CNN to determine both merge and split decisions.
This allows us to better tune our parameters with the scarce number of training examples from error correction.
Figure~\ref{fig:proposed-pipeline} shows our proposed framework that corrects both merge and split errors.

>>>>

% !TEX root =  paper.tex
\section{Proposed Work}

There are significantly more biological constraints that we plan to use in the future.
Once we improve our synaptic classifiers, we can ensure that we do not merge dendritic spines with axons. 
By stipulating that a segment on one side of the cell body can only have either pre- or post-synaptic connections, we will prevent undersegmentation that merges multiple neurons together.
Additionally, once we have a classifier to label each neuron as inhibitory or excitatory, we can prevent the merging of two different types of neurons.
Both of these additional constraints will help with the current problem associated with large-scale reconstruction.
That is, a small percentage of merge errors results in a tangled mess of multiple neurons per segment.

To further prevent this problem of undersegmentation, we will augment our current work to correct merge errors as well.
Generally, correcting merge errors is more difficult than correcting split errors because the space of possible split candidates grows quickly~\cite{parag2015properties}. 
However, we plan to prune these candidates more efficiently using a skeleton based method that considers the underlying biology.
Consider Figure~\ref{fig:proposal} that shows an incorrectly merged segment consisting a few neurons.
We can extract a coarser skeleton from this segment that does not hit every spine but still gets the general shape.
In particular, it shows three main paths in this one segment.

Once locating these potentially erroneous segments, we will run a watershed algorithm on the affinities that forces the voxels into two segments.
The surface separating the two segments is our ``split'' candidate.
We will extract a cubic region of interest around this candidate and input the region into our previously discussed merge classifier.
If the classifier suggests that the segments belong to one neuron, we will ignore the split candidate.
Otherwise we will divide this segment based on the candidate.
With a synaptic classifier, we can further constrain the watershed algorithm to only propose splits where pre- or post-synaptic connections occur on one side.
